Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-02-19 papers/wdmerger_I/paper.tex
Mention in the paper the ambiguity presented by whether we apply the rotation force before or after the gravitation force.

>>>>

We apply the rotation forces after the gravitation forces, but 
there is some freedom in the order in which to apply the gravitational and rotational terms.
This order may matter because the Coriolis force depends on the fluid velocity, and 
in the predictor-corrector approach, we use the velocities both at 
time-level $n$ and time-level $n+1$. If we update the latter with the gravitational force, 
then the Coriolis force will see a different velocity than the one obtained through the 
pure hydrodynamics step. (This does not matter for the energy equation in our new formulation,
because the velocities used are always the time-level $n+1/2$ values coming from the Riemann solver.)
In practice, this will not matter significantly for our simulations in this work 
because the centrifugal force plays the dominant role in maintaining stability of non-contact 
binary systems, and the centrifugal force does not depend on the fluid velocity.
However, this issue may be worth exploring in future work in situations where the Coriolis 
term is non-negligible in determining the system evolution.
